Stateless Model Checking with Data-Race Preemption Points

### 2016-07-19 oopsla-16/paper.tex
refactor design section intro and write algorithm0
forgot stupid changebar package breaks 2col tables
deanonymize

\documentclass[10pt,times,numbers]{sigplanconf}
\usepackage[1stsubmission]{oopsla2016}

@@

\usepackage{amsmath}
\usepackage{url}
\usepackage{enumitem}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}

@@

%\newcommand\revision[1]{\begin{samepage}\cbstart#1\cbend\end{samepage}}
%\newcommand\revision[1]{\cbstart#1\cbend}
\newcommand\revision[1]{#1}
\definecolor{purple}{RGB}{192,0,192}
%\newcommand\revision[1]{\hilight{purple}{#1}}

@@

% TODO CAMREADY: Make data set, at least, public.

{\em github links removed for double-blind review}
%\url{https://github.com/bblum/landslide} % POST-SUBMISSION TODO: put QS in its own repository
%
%\url{https://github.com/bblum/landslide} % POST-SUBMISSION TODO: put final logs somewhere
% TODO CAMREADY: Don't forget to anonymize the names of all your grupos.

@@

% TODO CAMREADY
%{\em removed for double-blind review}
%Many thanks to Vaishaal Shankar, Haryadi Gunawi, and David A. Eckhardt for generously providing student implementations from Berkeley's, U. of chicago's, and CMU's OS classes respectively.
%Thanks to Wind River for the use of their simulator \simics.
%Thanks to
%Ji\v{r}\'{i} \v{S}im\v{s}a, Joshua Wise, Jean Yang, Brandon Lucia, Haryadi Gunawi, John Wilkes, and
%the anonymous PLDI reviewers for their helpful comments.
%This work was supported in part by
%the U.S. Army Research Office under grant number W911NF0910273.

@@

%Acknowledgments, if needed.
{\em omitted for double-blind review}

>>>>

\documentclass[10pt,times,numbers]{sigplanconf}
\usepackage[2ndsubmission]{oopsla2016}

@@

\usepackage{amsmath}
\usepackage{url}
\usepackage{enumitem}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{amsthm}
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}

@@

\newcommand\revision[1]{#1}
\definecolor{purple}{RGB}{192,0,192}
\newcommand\revisionx[1]{\hilight{purple}{#1}\xspace}
%\newcommand\revision[1]{\hilight{purple}{#1}}

@@

\url{https://github.com/bblum/oopsla-quicksand}
% TODO CAMREADY: Make data set, at least, public.
\url{https://github.com/bblum/oopsla-dataset}

% TODO CAMREADY: Don't forget to anonymize the names of all your grupos.

@@

@@

Many thanks to Vaishaal Shankar, Haryadi Gunawi, and David A. Eckhardt for generously providing student implementations from Berkeley's, U. of Chicago's, and CMU's OS classes respectively.
Thanks to Wind River for the use of their simulator \simics.
Thanks to
Ji\v{r}\'{i} \v{S}im\v{s}a, Joshua Wise, Jean Yang, Brandon Lucia, Haryadi Gunawi, John Wilkes, and
the anonymous OOPSLA reviewers for their helpful comments.
This work was supported in part by
the U.S. Army Research Office under grant number W911NF0910273.
